\documentclass[../main.tex]{subfiles}
	% COMMUNICATIONS TESTING
\begin{document}

\todo[inline,color=blue!20]{Neet to write up the Comms Testing -- Mention the fact that we had to deal with deletion channel vs error channel, clocked vs unclocked, Justin's project - http://diwine-project.eu/public/publications.html}

Testing Communications, remember project levels:\\

\begin{quotation}
	\textbf{Easily Attainable:}
	Construct a basic wired unidirectional communication test bed complete with a transmitter and a receiver.
	These units should be synchronised and an appropriate line code (i.e., baseband modulation scheme) should be exploited to convey test data from one device to another.\\
	
	\textbf{Medium Complexity:}
	Characterise the performance of the test bed, identifying bandwidth limitations, noise characteristics, and reliability for different modulation and coding schemes. Test specific state-of-the-art modulation techniques recently published in the research literature. (These will be identified by the supervisor).\\
	
	\textbf{Advanced:}
	Develop design enhancements that will enable the test bed to be extended to wireless scenarios, including RF and optical wireless systems.
	Implement these modifications if the budget permits.
\end{quotation}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{SNR for Different Modulation Schemes}

\todo[inline]{I'm not entirely clear on how you would calculate the SNR for these signals, considering we end up with a bit stream on either end and so bit error rate is easy to understand. Some insight as I'm writing up the test results would be handy -- An SNR measurement assumes there is noise in the system.  If you measure noise naturally, or otherwise artificially generate it, then the SNR would be E[wanted signal power]/E[noise signal power].}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Error Rate}

Bit error rate of transmission.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Channel Coding} \label{sec_Channel Coding}

Syndrome decoding - not a large amount of it covered but rather interesting stuff!

\end{document}